Presentation Title

### 2017-07-31 thesis/chapters/ch3-model.tex
Write conclusion and fix references

We design a novel system in order to achieve our ambitious goals outline in~\Cref{ch:problem}.
The system consist of three protocols---the consensus protocol, the transaction protocol and the validation protocol.
It is based on our prior work on TrustChain~\cite{trustchain}, where every node independently interact with each other via their own blockchain.

@@

\subsection{Extended TrustChain}
Extended TrustChain naturally builds on top of the standard TrustChain. 
Thus we first describe the standard TrustChain.
Our description has minor differences compared to the description in~\cite{trustchain}.
This is to help with the description of the extended TrustChain.
We remark the difference when it occurs.
However, the two descriptions are functionally the same.

\subsubsection*{Standard TrustChain}
In TrustChain, every node has a ``personal'' chain. 
Initially, the chain only contains a genesis block generated by the nodes themselves.
When a node $A$ wishes to add a new transaction (TX) with $B$,
a new TX block is generated for both $A$ and $B$ and is appended to their respective chains.
The TX block must have a valid hash pointer pointing to the previous block
and a reference\footnote{This is different from the original TrustChain definition found in~\cite{trustchain}.
In there, a TX block has two outgoing edges which are hash pointers to the two parties involved in the transaction.
This work uses one outgoing edge and a reference.} to its \emph{pair} on $B$'s chain.
An example of is shown in \Cref{fig:trustchain-bad}.

@@

\subsection{Using timing assumption in the permissionless setting}
Our model is purely asynchronous, where we make no timing assumptions anywhere in the protocol.
In many applications however, it is often fine to make timing assumptions.
For example, TCP relies on timeout for its retransmission and the \texttt{nLockTime} property in Bitcoin transactions makes the transaction unspendable until some time in the future (either Unix time or block height)~\cite{bitcoindevguide}.
One limitation of our system is that we use the parameter $N$ in our algorithms, which makes it unsuitable for the permissionless environment where users can join and leave at will.
In this section we show how making a timing assumption would allow us to operate in the permissionless setting.

>>>>

We design a novel system in order to achieve our ambitious goals outline in~\Cref{ch:problem}.
The system consist of three protocols---the consensus protocol, the transaction protocol and the validation protocol.
It is based on our prior work on TrustChain~\cite{multichain},
where every node independently interact with each other via their own blockchain\footnote{It is originally called MultiChain but the name has changed to TrustChain}.

@@

\subsection{Extended TrustChain}
Extended TrustChain naturally builds on top of the standard TrustChain. 
Thus we first describe the standard TrustChain.
Our description has minor differences compared to the description in~\cite{multichain}.
This is to help with the description of the extended TrustChain.
We remark the difference when it occurs.
However, the two descriptions are functionally the same.

\subsubsection*{Standard TrustChain}
In TrustChain, every node has a ``personal'' chain. 
Initially, the chain only contains a genesis block generated by the nodes themselves.
When a node $A$ wishes to add a new transaction (TX) with $B$,
a new TX block is generated for both $A$ and $B$ and is appended to their respective chains.
The TX block must have a valid hash pointer pointing to the previous block
and a reference\footnote{This is different from the original TrustChain definition found in~\cite{multichain}.
In there, a TX block has two outgoing edges which are hash pointers to the two parties involved in the transaction.
This work uses one outgoing edge and a reference.} to its \emph{pair} on $B$'s chain.
An example of is shown in \Cref{fig:trustchain-bad}.

@@

\subsection{Using timing assumption in the permissionless setting}
\label{sec:permissionless}
Our model is purely asynchronous, where we make no timing assumptions anywhere in the protocol.
In many applications however, it is often fine to make timing assumptions.
For example, TCP relies on timeout for its retransmission and the \texttt{nLockTime} property in Bitcoin transactions makes the transaction unspendable until some time in the future (either Unix time or block height)~\cite{bitcoindevguide}.
One limitation of our system is that we use the parameter $N$ in our algorithms, which makes it unsuitable for the permissionless environment where users can join and leave at will.
In this section we show how making a timing assumption would allow us to operate in the permissionless setting.

### 2017-07-31 thesis/chapters/ch7-conclusion.tex
Write conclusion and fix references

\section{Future work}

>>>>

The research question we asked in~\Cref{ch:problem} is the following.
\begin{displayquote}
\emph{Is it possible to design a blockchain consensus protocol that is fault tolerant, scalable and can reach global consensus?}
\end{displayquote}
We answer it in the affirmative and our system achieves all the requirements.
Fault tolerance is guaranteed if $n \ge 3t + 1$ from ACS.
While $t$ may be small compared to the population size $N$,
we show that the probability for the system to fail is low even when $n \ge 3t + 1$ does not hold as long as the proportion of malicious nodes is not close to a third of $N$.
Horizontal scalability is demonstrated both analytically and experimentally.
With 1200 nodes in the network we were able to achieve nearly 5000 TX/s---an order of magnitude improvement over Bitcoin.
Finally, we achieve global consensus on transactions via consensus on checkpoint blocks.

This work is the first step in building a new paradigm for blockchain consensus protocol.
It has the potential to efficiently cultivate trust on the internet in the presence of faults without any central authority.
We hope to improve our design by building a concrete application on top of it.

\section{Future work}
While our system has excellent scalability properties, it is not without limitations.
Much of it is from the fact that it does not have a concrete application.
We do not attempt to prevent the Sybil attack, spam or DoS because the accuracy of the defence depends on the understanding of the application.
For instance, without any application it would be impossible to distinguish between a very active node from a spammer because the content of the transaction ($m$) carry no meaning.

Our experiment is carried out in a somewhat idealised world (DAS-5).
To understand our system further, we hope to experiment on a real platform with real users such as Tribler~\cite{pouwelse2008tribler}.
For instance, the TrustChain in Tribler stores the number of bytes uploaded and downloaded between users, but it has no global consensus.
It would be useful to integrate our consensus protocol into Tribler to prevent misreporting attacks.
More importantly it gives us an opportunity to observe the characteristics of our system in the real world and how it evolves with new features or alterations.

The fault tolerance property of our system is lower than that of typical blockchain systems,
which usually aim for fewer than 50\%.
For future work, we propose the following two ways to improve fault tolerance.
First, use a reputation mechanism to select facilitators rather than simply selecting them randomly so that faulty nodes are less likely to be selected.
This technique of course heavily depends on the application,
for P2P file sharing systems the reputation score may be the number of bytes contributed to the network.
Second, instead of using ACS we use a proof-of-stake (PoS) scheme which means that nodes with more stake in the system gets more vote.
In an ideal PoS scheme, the system can tolerate any fault if the majority of the stake holders are honest.

Finally, as mentioned in~\Cref{sec:permissionless}, we wish to evaluate our system (analytically and experimentally) in the permissionless settings.
This would enable our protocol to be applied to a much wider range of applications.
